Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-24 cav2017/cav2017.tex
nudge

In this work, we propose the synthesis of \emph{safe} control algorithms for
LTI models taking into consideration the continuous domain of the plant, 
alongside the discrete domain of the controller, 
as well as the hybrid elements that relate them.  
%% In this paper, we synthesize controllers for hybrid
%% closed-loop systems, i.e., software-implemented embedded controllers along
%% with a model of their physical environment (the plant), that are
%% \emph{safe}.
Due to the complexity of such systems, in this work we focus 
on linear models with known  implementation features (e.g., number of bits, fixed-point
arithmetic), %\addtodo{[clarify next] with known configurations} 
and perform %parametric 
synthesis of safe digital controllers - the extension to more general quantitative properties is left to future work.

@@

There are two different problems that arise from FWL semantics.  The first
is the error in the dynamics caused by the inability to represent the exact
state of the physical system, while the second relates to rounding errors
during computation.  In~\cite{fialho1994stability}, a stability measure
based on the error of the digital dynamics ensures that the deviation
introduced by FWL does not make the digital system unstable.  A more recent
approach~\cite{DBLP:journals/automatica/WuLCC09} uses $\mu$ calculus to
directly model the digital controller so that the selected parameters are
stable by design.  The analyses in~\cite{DBLP:conf/hybrid/RouxJG15,
DBLP:conf/hybrid/WangGRJF16} rely on an invariant computation on the
discrete system dynamics using Semi-Definite Programming (SDP).  While the
former uses BIBO properties to determine stability, the latter uses
Lyapunov-based quadratic invariants.  In both cases, the SDP solver uses
floating-point arithmetic and soundness is checked by bounding the error. 
An alternative approach is taken by~\cite{park2016scalable}, where the
verification of given control code is performed against a known model by
extracting an LTI model of the code through symbolic execution.  In order to
account for rounding errors, an upper bound is introduced in the
verification phase.  The work in \cite{picasso2003stabilization,
picasso2002construction} introduces attractive invariant sets as a mechanism
to bound the quantization error effect on stabilisation as an invariant set
that always converges toward the controllable set.  In a similar fashion,
\cite{liberzon2003hybrid} evaluates the dynamics of the quantization error
and bounds its trajectory to a known region over a finite period of time. 
This technique works for both linear and non-linear systems.

@@

In this study, we are not limited to the synthesis of digital stabilizing controllers -- 
a well known task in the literature on digital control system -- 
but target safety requirements with an overall approach that is sound and automated. 
More specifically, 
we require that the closed-loop system \eqref{eq:closedloopss} meets given safety specifications. 
A safety specification raises a requirement on the states of the model, 
such that the feedback controller (namely the choice of the gains in $K$) 
must ensure that the states never exit such requirement. 
Note that a stable, closed-loop system is not necessarily a safe system: 
indeed, the state values may leave the safe space whilst they converge to the equilibrium, 
which is typical in the case of oscillatory dynamics. However, a safe system will always be stable.
In this work, the safety property represented by $\phi_{safety}$ is encoded as follows: 
%
\begin{equation}
\label{eq:safetyliteral}
\phi_{safety}\iff \forall k\geq 0, \bigwedge_{i=1}^{n}{\underline{x_{i}} \leq x_{i,k} \leq \overline{x_{i}}},
\end{equation}
%
%\addtodo{We consider $x_{i}^{-}$ and $x_{i}^{+}$ to be -1 and 1, respectively.}
where $\underline{x_{i}}$ and $\overline{x_{i}}$ are lower and upper bounds for the $i$-th coordinate $x_{i}$ of state $x\in \mathbb R^n$ at the $k$-th instant, respectively. 
This means that the states will always be within the $n$-dimensional hyper-box.

>>>>

In this work, we propose the synthesis of \emph{safe} control algorithms for
LTI models taking into consideration the continuous domain of the plant, 
alongside the discrete domain of the controller, 
as well as the hybrid elements that relate them.  
%% In this paper, we synthesize controllers for hybrid
%% closed-loop systems, i.e., software-implemented embedded controllers along
%% with a model of their physical environment (the plant), that are
%% \emph{safe}.
Due to the complexity of such systems, in this work we focus 
on linear models with known  implementation features (e.g., number of bits, fixed-point
arithmetic), %\addtodo{[clarify next] with known configurations} 
and perform %parametric 
synthesis of safe digital controllers -- the extension to more general
quantitative properties is left to future work.

@@

There are two different problems that arise from FWL semantics.  The first
is the error in the dynamics caused by the inability to represent the exact
state of the physical system, while the second relates to rounding errors
during computation.  In~\cite{fialho1994stability}, a stability measure
based on the error of the digital dynamics ensures that the deviation
introduced by FWL does not make the digital system unstable.  A~more recent
approach~\cite{DBLP:journals/automatica/WuLCC09} uses $\mu$ calculus to
directly model the digital controller so that the selected parameters are
stable by design.  The analyses in~\cite{DBLP:conf/hybrid/RouxJG15,
DBLP:conf/hybrid/WangGRJF16} rely on an invariant computation on the
discrete system dynamics using Semi-Definite Programming (SDP).  While the
former uses BIBO properties to determine stability, the latter uses
Lyapunov-based quadratic invariants.  In both cases, the SDP solver uses
floating-point arithmetic and soundness is checked by bounding the error. 
An alternative approach is taken by~\cite{park2016scalable}, where the
verification of given control code is performed against a known model by
extracting an LTI model of the code through symbolic execution.  In order to
account for rounding errors, an upper bound is introduced in the
verification phase.  The work in \cite{picasso2003stabilization,
picasso2002construction} introduces attractive invariant sets as a mechanism
to bound the quantization error effect on stabilisation as an invariant set
that always converges toward the controllable set.  In a similar fashion,
\cite{liberzon2003hybrid} evaluates the dynamics of the quantization error
and bounds its trajectory to a known region over a finite period of time. 
This technique works for both linear and non-linear systems.

@@

In this study, we are not limited to the synthesis of digital stabilizing
controllers -- a well known task in the literature on digital control system
-- but target safety requirements with an overall approach that is sound and
automated.  More specifically, we require that the closed-loop system
\eqref{eq:closedloopss} meets given safety specifications.  A safety
specification raises a requirement on the states of the model, such that the
feedback controller (namely the choice of the gains in $K$) must ensure that
the states never exit such requirement.  Note that a stable, closed-loop
system is not necessarily a safe system: indeed, the state values may leave
the safe space whilst they converge to the equilibrium, which is typical in
the case of oscillatory dynamics.  However, a safe system will always be
stable.  In~this work, the safety property represented by $\phi_{safety}$ is
encoded as follows:
%
\begin{equation}
\label{eq:safetyliteral}
\phi_{safety}\iff \forall k\geq 0, \bigwedge_{i=1}^{n}{\underline{x_{i}} \leq x_{i,k} \leq \overline{x_{i}}},
\end{equation}
%
%\addtodo{We consider $x_{i}^{-}$ and $x_{i}^{+}$ to be -1 and 1, respectively.}
%
where $\underline{x_{i}}$ and $\overline{x_{i}}$ are lower and upper bounds
for the $i$-th coordinate $x_{i}$ of state $x\in \mathbb R^n$ at the $k$-th
instant, respectively.  This means that the states will always be within the
$n$-dimensional hyper-box.
